---
title: "Guardian_Text_Mining"
author: "Swagata Chakraborty"
date: "6/21/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#install.packages("jsonlite")
library(jsonlite)
library(purrr)
library(tidyverse)
library(ggmap)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(scales)
library(lubridate)
library(forcats)
library(tm)
library(tidytext)
library(wordcloud)
library(ggplot2)
library(scales)
```

Load File:
```{r}
path <-  "/Users/swagatachakraborty/Documents/sc53711/Applications/Universities/UCSD/Assignments/Hansen_Project/articles"
files <- dir(path, pattern = "*.json")
data <- files %>%
       map_df(~fromJSON(file.path(path, .), flatten = TRUE))
```

# Document Term Matrix (DTM): 

Document Term Matrix: This is an array where each row corresponds to a document and each column corresponds to a word. The entries of the array are simply counts of how many times a certain word occurs in a certain document. 

Topic wise word clouds:
```{r}
## we have 86 granular categories
#table(my_data$sectionId) %>% as.data.frame() %>% arrange(desc(Freq))

## narrowed categories:
# world+global
# commentfree
# sport+ football
# country_news: uk_news + australia_news+ us_news +news
# tv_radio & films & music & fashion & artanddesign
# society & lifestyle & culture
# business + business-to-business
# politics + law
# books 
# education + higher-education-network + teacher-network
# technology & science
# environment
# travel
# healthcare-network

my_data <-  data %>% 
            filter(sectionId %in% c("world",
                                    "global",
                                    "sport",
                                    "football",
                                    "uk-news","australia-news","us-news","news",
                                    "tv-and-radio","film","music","fashion","artanddesign",
                                    "society" , "lifeandstyle" , "culture",
                                    "business","business-to-business",
                                    "politics" , "law",
                                    "books", "education","higher-education-network" , "teacher-network",
                                    "technology" , "science",
                                    "environment",
                                    "travel",
                                    "healthcare-network")
                   )

my_data$group <- my_data$sectionId


my_data[(my_data$sectionId %in% c("world", "global")),"group"] <- "world"
my_data[(my_data$sectionId %in% c("sport", "football")),"group"] <- "sports"
my_data[(my_data$sectionId %in% c("uk-news","australia-news","us-news","news")),"group"] <- "general_news"
my_data[(my_data$sectionId %in% c("tv-and-radio","film","music","fashion","artanddesign")),"group"] <- "entertainment_art"
my_data[(my_data$sectionId %in% c("society" , "lifeandstyle" , "culture")),"group"] <- "lifestyle_cult"
my_data[(my_data$sectionId %in% c("business","business-to-business")),"group"] <- "business"
my_data[ (my_data$sectionId %in% c("politics" , "law")),"group"] <- "politics_law"
my_data[(my_data$sectionId %in% c("books", "education","higher-education-network" , "teacher-network")),"group"] <- "education"
my_data[(my_data$sectionId %in% c("technology" , "science")),"group"] <- "tech_science"

table(my_data$group) %>% as.data.frame() %>% arrange(desc(Freq))
#my_data <- my_data %>% rename(id=doc_id,fields.bodyText=text )


my_data_new <-my_data %>% group_by(group) %>% sample_frac(.3)

colnames(my_data_new)[1] <- "doc_id"
colnames(my_data_new)[31] <- "text"


## shorten analysis: sample 10% rows from each category:


## text part of each doc
#text.c <- VCorpus(DataframeSource(select(my_data,doc_id,text)))


docs <- data.frame(doc_id = my_data_new$doc_id,
                   text = my_data_new$text,
                   stringsAsFactors = FALSE)
#(ds <- DataframeSource(docs))
x <- VCorpus(DataframeSource(docs))
# inspect(x)
# meta(x)


## DTM of the  text part of each Doc
DTM <- DocumentTermMatrix(x,
                          control=list(removePunctuation=TRUE,
                                       wordLengths=c(3, Inf),
                                       stopwords=TRUE,
                                       stemming=TRUE,
                                       removeNumbers=TRUE
                                       ))

DTM.sp <- removeSparseTerms(DTM,0.995)
#inspect(DTM.sp)

```



## Visualization of common words

1.) bar plot
```{r}
text.tidy <- tidy(DTM.sp)

term.count <- text.tidy %>%
              group_by(term) %>%
              summarize(n.total=sum(count)) %>%
              arrange(desc(n.total))

## top 30 words
term.count %>% 
  slice(20:50) %>%
  ggplot(aes(x=fct_reorder(term,n.total),y=n.total)) + geom_bar(stat='identity') + 
  coord_flip() + xlab('Counts') + ylab('')+ggtitle('Most Frequent Terms')
```

\  
\  

2.) word cloud
```{r}
#top 95 words
term.count.pop <- term.count %>% slice(20:100) 
wordcloud(term.count.pop$term, term.count.pop$n.total, scale=c(5,.5))
```

\  
\  
\  

## Visualization of sentiment analysis
```{r}
# text.tidy, creates table of doc*term frequency
ap_sentiments <- text.tidy %>%
  inner_join(get_sentiments("bing"), by = c(term = "word"))



ap_sentiments %>%
  count(sentiment, term, wt = count) %>%
  ungroup() %>%
  filter(n >= 20 & n <=25) %>%  # we'hv subset a very few words only because we wanted to visualize clearly and understand the code
  mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
  mutate(term = reorder(term, n)) %>%
  ggplot(aes(term, n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  ylab("Contribution to sentiment") +
  coord_flip()
```
\  
\  

## TF- IDF

TF-IDF: We may be interested in finding the words most specific to each of the inaugural speeches. This could be quantified by calculating the tf-idf of each term-speech pair using the bind_tf_idf().

The statistic tf-idf identifies words that are important to a document in a collection of documents; in this case, we’ll see which words are important in one of the documents compared to the others.
```{r}
text_tf_idf <- text.tidy %>%
  count(document, term, sort = TRUE) %>%
  bind_tf_idf(term, document, count) %>%
  arrange(desc(tf_idf)) %>% 
  group_by(document) %>%
  top_n(10) %>%
  ungroup

## pick top documents
doc_list <-text_tf_idf %>% group_by(document) %>% summarise(freq=n()) %>% arrange(-freq) %>% slice(1:6)

##library(drlib) unable to install, using the functions desc itself below:
reorder_within <- function(x, by, within, fun = mean, sep = "___", ...) {
  new_x <- paste(x, within, sep = sep)
  stats::reorder(new_x, by, FUN = fun)
}

scale_x_reordered <- function(..., sep = "___") {
  reg <- paste0(sep, ".+$")
  ggplot2::scale_x_discrete(labels = function(x) gsub(reg, "", x), ...)
}

## trial
for (doc_temp in (doc_list$document)) {
p <-text_tf_idf %>%
    filter(document %in% doc_temp) %>% 
    mutate(term = reorder_within(term, tf_idf, document)) %>%
    slice(1:25) %>% 
    ggplot(aes(term, tf_idf, fill = document)) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    #facet_wrap(~ document, scales = "free", ncol = 3) +
    scale_x_reordered() +
    coord_flip() +
    theme(strip.text=element_text(size=11)) +
    labs(x = NULL, y = "tf-idf",
         title = "Highest tf-idf words in popular articles",
         subtitle = paste("doc_type",doc_temp))

print(p)
}

```



```{r}
# sort the data frame and convert word to a factor column
plot_article <- text_tf_idf %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(term, levels = rev(unique(term))))
  group_by(document) %>%
  top_n(10) %>%
  ungroup() %>% 

head(plot_article)

# graph the top 10 tokens for 4 categories

for (group_temp in unique(my_data_new$group)) {
  p <- plot_article %>%
  left_join(my_data_new[,c("doc_id","group")], by = c("document" = "doc_id")) %>% 
  filter(group %in% group_temp) %>% 
  arrange(group,desc(tf_idf)) %>% 
  #group_by(group) %>%
  slice(1:10) %>%
  #ungroup() %>%
  ggplot(aes(word, tf_idf)) +
  theme_classic()+
  geom_col() +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~group, scales = "free") +
  coord_flip() +
  labs(
         title = "Highest tf-idf words in different category of articles",
         subtitle = paste("acrticle category: ",group_temp))
  
  print(p)
}

  
  
  plot_article %>%
  left_join(my_data_new[,c("doc_id","group")], by = c("document" = "doc_id")) %>% 
  filter(group %in% c("entertainment_art")) %>% 
  arrange(desc(tf_idf)) %>% 
  #group_by(group) %>%
  slice(1:25) %>%
  #ungroup() %>%
  ggplot(aes(word, tf_idf)) +
  geom_col() +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~group, scales = "free") +
  coord_flip()
  
  

```


```{r}
library(tidyr)

year_term_counts <- text.tidy %>%
  left_join(my_data[,c("doc_id","fields.lastModified")],by = c("document" = "doc_id")) %>% 
  mutate(fields.lastModified=substr(fields.lastModified, 1, 10)) %>% 
  complete(fields.lastModified, term, fill = list(count = 0)) %>%
  group_by(fields.lastModified) %>%
  mutate(year_total = sum(count))
  
year_term_counts %>%
  filter(term %in% c("abort", "attack", "crime", "cancer", "work", "trump")) %>%
  ggplot(aes(fields.lastModified, count / year_total)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~ term, scales = "free_y") +
  scale_y_continuous(labels = scales::percent_format()) +
  ylab("% frequency of word in inaugural address")
```

 
## TOPIC MODELING:

```{r}
library(quanteda)
library(stm)
#install.packages("stm")

article_dfm <- text.tidy %>%
    count(document, term, sort = TRUE) %>%
    cast_dfm(document, term, n)

article_sparse <- text.tidy %>%
    count(document, term, sort = TRUE) %>%
    cast_sparse(document, term, n)


topic_model <- stm(article_sparse, K = 8, 
                   verbose = FALSE, init.type = "Spectral")
```

Plot Visualization:
```{r}
td_beta <- tidy(topic_model)

td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    labs(x = NULL, y = expression(beta),
         title = "Highest word probabilities for each topic",
         subtitle = "Different words are associated with different topics")
```

